Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-04-03 manuscript.qmd
use custom fig-/fontsizes

import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
from tueplots import figsizes, fontsizes

@@

plt.rcParams.update(figsizes.icml2024_full(nrows=nrows, ncols=ncols))
plt.rcParams.update(fontsizes.icml2024())

@@

```{python}
#| echo: false
#| label: fig-burnin-history
#| layout-ncol: 1
#| layout-nrow: 1
#| fig-cap: Monitoring quantities during the burn-in phase of the parameter sampling.
from collections import namedtuple

nrows, ncols = 1, 3
label_map = {
  "acor_times": "Autocorrelation [steps]",
  "accept_fracs": "Sample Acceptance [%]",
  "max_log_probs": "Maximum log-Likelihood",
}

plt.rcParams.update(figsizes.icml2024_full(nrows=nrows, ncols=ncols))
plt.rcParams.update(fontsizes.icml2024())

@@

for model in ["ipsi", "contra", "bilateral", "midline"]:
  history = pd.read_csv(f"models/{model}/history.csv").set_index("steps")
  for i, column in enumerate(history.columns):
    history.plot(y=column, ax=axes[i], label=model)
    axes[i].autoscale(enable=True, tight=True, axis="x")
    axes[i].set_title(label_map[column])

plt.show()
```

@@

```{python}
#| echo: false
#| label: fig-prevalences
#| fig-cap: Prevalences of different scenarios.
from lyscripts.scenario import Scenario
from lyscripts.plot.utils import draw, BetaPosterior, Histogram, COLOR_CYCLE

@@

@@

content = []
color = next(COLOR_CYCLE)
content += [
  Histogram.from_hdf5(
    filename=paths.get_filename(model="midline", kind="prevalences"),
    dataname=scenarios[0].md5_hash("prevalences"),
    color=color,
  ),
  BetaPosterior.from_hdf5(
    filename=paths.get_filename(model="midline", kind="prevalences"),
    dataname=scenarios[0].md5_hash("prevalences"),
  ),
]
color = next(COLOR_CYCLE)
content += [
  Histogram.from_hdf5(
    filename=paths.get_filename(model="midline", kind="prevalences"),
    dataname=scenarios[1].md5_hash("prevalences"),
    color=color,
  ),
  BetaPosterior.from_hdf5(
    filename=paths.get_filename(model="midline", kind="prevalences"),
    dataname=scenarios[1].md5_hash("prevalences"),
  ),
]
draw(
  axes=ax,
  contents=content,
  percent_lims=(2., 2.),
)
```

@@

early_midext_prob = model.get_distribution("early").pmf @ model.midext_evo()[:,1]
late_midext_prob = model.get_distribution("late").pmf @ model.midext_evo()[:,1]

>>>>

import pandas as pd
import numpy as np
import matplotlib.pyplot as plt
from matplotlib import ticker

@@

plt.rcParams.update(shared.get_fontsizes())
plt.rcParams.update(shared.get_figsizes(nrows=nrows, ncols=ncols))

@@

```{python}
#| echo: false
#| label: fig-burnin-history 
#| fig-cap: Monitoring quantities during the burn-in phase of the parameter sampling.
from collections import namedtuple

def custom(x, pos):
  return "{:.1f}".format(x/1000)

nrows, ncols = 1, 3
label_map = {
  "acor_times": "autocorrelation [steps]",
  "accept_fracs": "acceptance fraction [%]",
  "max_log_probs": r"max. log-likelihood [$\times 10^3$]",
}

plt.rcParams.update(shared.get_fontsizes())
plt.rcParams.update(shared.get_figsizes(nrows=nrows, ncols=ncols, aspect_ratio=1.))

@@

for model in ["ipsi", "contra", "bilateral", "midline"]:
  history = pd.read_csv(f"models/{model}/history.csv").set_index("steps")
  for i, column in enumerate(history.columns):
    history.plot(y=column, ax=axes[i], label=model)
    axes[i].autoscale(enable=True, tight=True, axis="x")
    axes[i].set_ylabel(label_map[column])
    axes[i].xaxis.set_major_formatter(ticker.FuncFormatter(custom))
    axes[i].set_xlabel(r"steps [$\times 10^3$]")

axes[1].yaxis.set_major_formatter(ticker.StrMethodFormatter("{x:.0%}"))
axes[2].yaxis.set_major_formatter(ticker.FuncFormatter(custom))
plt.show()
```

@@

```{python}
#| echo: false
#| label: fig-prevalences
#| fig-cap: Prevalences of different scenarios.
from lyscripts.scenario import Scenario
from lyscripts.plot.utils import draw, BetaPosterior, Histogram, COLORS

@@

plt.rcParams.update(shared.get_fontsizes())
plt.rcParams.update(shared.get_figsizes(aspect_ratio=2.))

@@

content = []
content += [
  Histogram.from_hdf5(
    filename=paths.get_filename(model="midline", kind="prevalences"),
    dataname=scenarios[0].md5_hash("prevalences"),
    color=COLORS["blue"],
  ),
  BetaPosterior.from_hdf5(
    filename=paths.get_filename(model="midline", kind="prevalences"),
    dataname=scenarios[0].md5_hash("prevalences"),
    color=COLORS["blue"],
  ),
]

content += [
  Histogram.from_hdf5(
    filename=paths.get_filename(model="midline", kind="prevalences"),
    dataname=scenarios[1].md5_hash("prevalences"),
    color=COLORS["orange"],
  ),
  BetaPosterior.from_hdf5(
    filename=paths.get_filename(model="midline", kind="prevalences"),
    dataname=scenarios[1].md5_hash("prevalences"),
    color=COLORS["orange"],
  ),
]
draw(
  axes=ax,
  contents=content,
  percent_lims=(2., 2.),
)
```

@@

early_midext_prob = model.state_dist(t_stage="early")[1].sum()
late_midext_prob = model.state_dist(t_stage="late")[1].sum()
